Geospatial - Assignment 1 - Moritz Peist, Noemi Lucchi, Simon Vellin

### 2025-01-27 hw1/submission_notebook.Rmd
minor updates

We retrieved population data from the aforementioned IBGE website and used geographical data available in the R package geobr. While the authors reproduced the same plot for three different years — 1950, 1980, and 2010 — due to a lack of data, we were only able to reproduce the plot for the most recent year. Specifically, on the IBGE website, we found data for 2009. However, we assume no significant variations in population occurred within a single year, allowing us to proceed with our analysis. For consistency, also the geographical data are referred to 2009.

@@

# Get the geographical data from the package geobr
state <- read_state(year=2009)
meso <- read_meso_region(year=2009)
```

>>>>

We retrieved population data from the aforementioned IBGE website and used geographical data available in the R package geobr. While the authors reproduced the same plot for three different years — 1950, 1980, and 2010 — due to a lack of data, we were only able to reproduce the plot for the most recent year. Specifically, on the IBGE website, we found data for 2009. However, we assume no significant variations in population occurred within a single year, allowing us to proceed with our analysis.

@@

# Get the geographical data from the package geobr
state <- read_state(year=2010)
meso <- read_meso_region(year=2010)
```
